Reproduce analyses reported in: *Phenotypic evolution is more constrained in simpler food webs*

### 2019-05-07 analyses/reproduce_analyses.Rmd
finished draft of revision and sent to Jordi for comments

# Gall size 
AF_uni_Diam <- RF_Diam$absolute_fitness %>% 
  select(-sc.log.Clutch, -sc.sqrt.Pref) %>%
  gather(ID, absolute_fitness, -sc.Diam, -Foodweb) %>%
  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>% 
  ggplot(., aes(x=sc.Diam, y=absolute_fitness, group=interaction(ID,Foodweb), color=Foodweb, alpha=ID_group, size=ID_group)) +
  geom_line() +
  scale_alpha_manual(values=c(1,0.2), guide=FALSE) +
  scale_size_manual(values=c(1.5,0.25), guide=FALSE) +
  xlab("Chamber diameter (SDs)") +
  ylab("Mean larval survival") +
  scale_color_manual(values = treatment_colors, name = "Food web") +
  scale_x_continuous(breaks=c(-1,-0.5,0,0.5,1), labels = c(-1,-0.5,0,0.5,1)) +
  scale_y_log10(breaks=uni_breaks, labels=uni_breaks) + annotation_logticks(sides = "l")+
  coord_cartesian(ylim=c(0.07,1))

@@

# Size x Clutch
AF_plot_Diam.Clutch <- RF_Diam.Clutch$absolute_fitness %>% 
  filter(Foodweb == "Complex") %>%
  ggplot(., aes(x=sc.Diam, y=sc.log.Clutch)) +
  geom_raster(aes(fill=average)) +
  stat_contour(aes(z = average), breaks = breaks["Complex"], linetype = "dotted", color = "black") +
  geom_raster(data = filter(RF_Diam.Clutch$absolute_fitness, Foodweb == "Simple"), aes(fill=average)) +
  stat_contour(data = filter(RF_Diam.Clutch$absolute_fitness, Foodweb == "Simple"), aes(z = average), breaks = breaks["Simple"], linetype = "dotted", color = "black") +
  facet_wrap(~Foodweb) +
  xlab("Gall diameter (SDs)") +
  ylab("Clutch size (SDs)") +
  scale_x_continuous(labels = c(-1,-0.5,0,0.5,1)) +
  scale_y_continuous(labels = c(-1,-0.5,0,0.5,1)) +
  scale_fill_viridis(name = "Mean larval\nsurvival", trans="log", breaks = my_breaks, labels = my_breaks, limits = c(AF_range$min, AF_range$max)) +
  theme(strip.background = element_blank(),
        strip.text.x=element_text(margin=margin(b=4)))

# Size x Preference
AF_plot_Diam.Pref <- RF_Diam.Pref$absolute_fitness %>% 
  filter(Foodweb == "Complex") %>%
  ggplot(., aes(x=sc.Diam, y=sc.sqrt.Pref)) +
  geom_raster(aes(fill=average)) +
  stat_contour(aes(z = average), breaks = breaks["Complex"], linetype = "dotted", color = "black") +
  geom_raster(data = filter(RF_Diam.Pref$absolute_fitness, Foodweb == "Simple"), aes(fill=average)) +
  stat_contour(data = filter(RF_Diam.Pref$absolute_fitness, Foodweb == "Simple"), aes(z = average), breaks = breaks["Simple"], linetype = "dotted", color = "black") +
  facet_wrap(~Foodweb) +
  xlab("Chamber diameter (SDs)") +
  ylab("Oviposition preference (SDs)") +
  scale_x_continuous(labels = c(-1,-0.5,0,0.5,1)) +
  scale_y_continuous(labels = c(-1,-0.5,0,0.5,1)) +
  scale_fill_viridis(name = "Mean larval\nsurvival", trans="log", breaks = my_breaks, labels = my_breaks, limits = c(AF_range$min, AF_range$max)) +
  theme(strip.background = element_blank(),
        strip.text.x=element_text(margin=margin(b=4)))

# Clutch x Preference
AF_plot_Clutch.Pref <- RF_Clutch.Pref$absolute_fitness %>%
  filter(Foodweb == "Complex") %>%
  ggplot(., aes(x=sc.sqrt.Pref, y=sc.log.Clutch)) +
  geom_raster(aes(fill=average)) +
  stat_contour(aes(z = average), breaks = breaks["Complex"], linetype = "dotted", color = "black") +
  geom_raster(data = filter(RF_Clutch.Pref$absolute_fitness, Foodweb == "Simple"), aes(fill=average)) +
  stat_contour(data = filter(RF_Clutch.Pref$absolute_fitness, Foodweb == "Simple"), aes(z = average), breaks = breaks["Simple"], linetype = "dotted", color = "black") +
  facet_wrap(~Foodweb) +
  xlab("Oviposition preference (SDs)") +
  ylab("Clutch size (SDs)") +
  scale_x_continuous(labels = c(-1,-0.5,0,0.5,1)) +
  scale_y_continuous(labels = c(-1,-0.5,0,0.5,1)) +
  scale_fill_viridis(name = "Mean larval\nsurvival", trans="log", breaks = my_breaks, labels = my_breaks, limits = c(AF_range$min, AF_range$max)) +
  theme(strip.background = element_blank(),
        strip.text.x=element_text(margin=margin(b=4)))

@@

eggptoid_selection_plot <- eggptoid_plot_df %>%
  ggplot(., aes(x=sc.sqrt.Pref, y=fitness_difference, group=ID, alpha=ID_group, size=ID_group)) +
  geom_line(color=cbPalette[5]) +
  scale_alpha_manual(values=c(1,0.2), guide=FALSE) +
  scale_size_manual(values=c(1.5,0.25), guide=FALSE) +
  xlab("Gall midge preference (SDs)") + 
  ylab(expression(paste(Delta," egg parasitoid survival (complex - simple)"))) +
  scale_x_continuous(breaks=c(-1,-0.5,0,0.5,1), labels = c(-1,-0.5,0,0.5,1)) +
  geom_hline(yintercept=0, linetype="dotted") +
  theme_cowplot(font_size = 12)

>>>>

# Gall size 
AF_uni_Diam <- RF_Diam$absolute_fitness %>% 
  select(-sc.log.Clutch, -sc.sqrt.Pref) %>%
  gather(ID, absolute_fitness, -sc.Diam, -Foodweb) %>%
  mutate(ID_group = ifelse(ID == "average", "average", "replicate"),
         Foodweb = factor(ifelse(Foodweb == "Complex", "Intact", "Extinction"), levels = c("Intact", "Extinction"))) %>% 
  ggplot(., aes(x=sc.Diam, y=absolute_fitness, group=interaction(ID,Foodweb), color=Foodweb, alpha=ID_group, size=ID_group)) +
  geom_line() +
  scale_alpha_manual(values=c(1,0.2), guide=FALSE) +
  scale_size_manual(values=c(1.5,0.25), guide=FALSE) +
  xlab("Chamber diameter (SDs)") +
  ylab("Mean larval survival") +
  scale_color_manual(values = treatment_colors, name = "Food web") +
  scale_x_continuous(breaks=c(-1,-0.5,0,0.5,1), labels = c(-1,-0.5,0,0.5,1)) +
  scale_y_log10(breaks=uni_breaks, labels=uni_breaks) + annotation_logticks(sides = "l")+
  coord_cartesian(ylim=c(0.07,1))

@@

labels_2D <- list("Complex"="Intact", "Simple"="Extinction")
labeller_2D <- function(variable, value) {
  return(labels_2D[value])
}

# Size x Clutch
AF_plot_Diam.Clutch <- RF_Diam.Clutch$absolute_fitness %>%
  filter(Foodweb == "Complex") %>%
  ggplot(., aes(x=sc.Diam, y=sc.log.Clutch)) +
  geom_raster(aes(fill=average)) +
  stat_contour(aes(z = average), breaks = breaks["Complex"], linetype = "dotted", color = "black") +
  geom_raster(data = filter(RF_Diam.Clutch$absolute_fitness, Foodweb == "Simple"), aes(fill=average)) +
  stat_contour(data = filter(RF_Diam.Clutch$absolute_fitness, Foodweb == "Simple"), aes(z = average), breaks = breaks["Simple"], linetype = "dotted", color = "black") +
  facet_wrap(~Foodweb, labeller = labeller_2D) +
  xlab("Gall diameter (SDs)") +
  ylab("Clutch size (SDs)") +
  scale_x_continuous(labels = c(-1,-0.5,0,0.5,1)) +
  scale_y_continuous(labels = c(-1,-0.5,0,0.5,1)) +
  scale_fill_viridis(name = "Mean larval\nsurvival", trans="log", breaks = my_breaks, labels = my_breaks, limits = c(AF_range$min, AF_range$max)) +
  theme(strip.background = element_blank(),
        strip.text.x=element_text(margin=margin(b=4)))

# Size x Preference
AF_plot_Diam.Pref <- RF_Diam.Pref$absolute_fitness %>% 
  filter(Foodweb == "Complex") %>%
  ggplot(., aes(x=sc.Diam, y=sc.sqrt.Pref)) +
  geom_raster(aes(fill=average)) +
  stat_contour(aes(z = average), breaks = breaks["Complex"], linetype = "dotted", color = "black") +
  geom_raster(data = filter(RF_Diam.Pref$absolute_fitness, Foodweb == "Simple"), aes(fill=average)) +
  stat_contour(data = filter(RF_Diam.Pref$absolute_fitness, Foodweb == "Simple"), aes(z = average), breaks = breaks["Simple"], linetype = "dotted", color = "black") +
  facet_wrap(~Foodweb, labeller = labeller_2D) +
  xlab("Chamber diameter (SDs)") +
  ylab("Oviposition preference (SDs)") +
  scale_x_continuous(labels = c(-1,-0.5,0,0.5,1)) +
  scale_y_continuous(labels = c(-1,-0.5,0,0.5,1)) +
  scale_fill_viridis(name = "Mean larval\nsurvival", trans="log", breaks = my_breaks, labels = my_breaks, limits = c(AF_range$min, AF_range$max)) +
  theme(strip.background = element_blank(),
        strip.text.x=element_text(margin=margin(b=4)))

# Clutch x Preference
AF_plot_Clutch.Pref <- RF_Clutch.Pref$absolute_fitness %>%
  filter(Foodweb == "Complex") %>%
  ggplot(., aes(x=sc.sqrt.Pref, y=sc.log.Clutch)) +
  geom_raster(aes(fill=average)) +
  stat_contour(aes(z = average), breaks = breaks["Complex"], linetype = "dotted", color = "black") +
  geom_raster(data = filter(RF_Clutch.Pref$absolute_fitness, Foodweb == "Simple"), aes(fill=average)) +
  stat_contour(data = filter(RF_Clutch.Pref$absolute_fitness, Foodweb == "Simple"), aes(z = average), breaks = breaks["Simple"], linetype = "dotted", color = "black") +
  facet_wrap(~Foodweb, labeller = labeller_2D) +
  xlab("Oviposition preference (SDs)") +
  ylab("Clutch size (SDs)") +
  scale_x_continuous(labels = c(-1,-0.5,0,0.5,1)) +
  scale_y_continuous(labels = c(-1,-0.5,0,0.5,1)) +
  scale_fill_viridis(name = "Mean larval\nsurvival", trans="log", breaks = my_breaks, labels = my_breaks, limits = c(AF_range$min, AF_range$max)) +
  theme(strip.background = element_blank(),
        strip.text.x=element_text(margin=margin(b=4)))

@@

eggptoid_selection_plot <- eggptoid_plot_df %>%
  ggplot(., aes(x=sc.sqrt.Pref, y=fitness_difference, group=ID, alpha=ID_group, size=ID_group)) +
  geom_line(color=cbPalette[5]) +
  scale_alpha_manual(values=c(1,0.2), guide=FALSE) +
  scale_size_manual(values=c(1.5,0.25), guide=FALSE) +
  xlab("Gall midge preference (SDs)") + 
  ylab(expression(paste(Delta," egg parasitoid survival (intact - extinction)"))) +
  scale_x_continuous(breaks=c(-1,-0.5,0,0.5,1), labels = c(-1,-0.5,0,0.5,1)) +
  geom_hline(yintercept=0, linetype="dotted") +
  theme_cowplot(font_size = 12)
